Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-23 article/ms.tex
in the midst of going through discussion based on conversations at SINS

This spread in metalicity is important: it strongly implies that the process responsible for this signature, rare as it is, is not necessarily tied to a certain epoch in the history of our galaxy. Rather, these stars appear to be continuously forming from successive generations of stars.

This argues against polluter candidates any theoretical hyper-massive Population III star that might be imagined. While such an object might be plausible in the context of NGC 2419, it cannot explain the enhanced K abundances observed in the disk at such a large spread in metalicity (assuming here no correlation between [Fe/H] and [K/Fe]), which implies formation of significant amounts K throughout the life of the galaxy.

@@

One possible scenario that could produce a large K enhanced signature throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is some less massive. The SAGB star then produces K, as well as possibly s-process neutron capture elements, and deposits its K rich envelope onto its smaller companion through conventional binary accretion. This smaller and companion would continue to evolve long after the SAGB star is gone and, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, would not. If the companion star had sufficient mass to undergo hot bottom burning, then Na should be enhanced from production from \ce{^24 Mg} and \ce{^22 Ne}. In this scenario, it is this smaller binary companion star that makes up our sample of 113 giants. Note that since the envelope in a hot-bottom burning star is well mixed, the spectral signatures of these elements are observable.

>>>>

This spread in metalicity is important: it implies that the process responsible for this signature, rare as it is, is not necessarily tied to a certain epoch in the history of our galaxy. Rather, these stars appear to be continuously forming from successive generations of stars.

This argues against any theoretical hyper-massive Population III star that might be imagined being the polluter candidate. While such an object might be plausible in the context of NGC 2419, and appealing given the uniqueness of the cluster, it cannot explain the enhanced K abundances observed in the disk at such a large spread in metalicity, which implies formation of significant amounts K throughout the life of the galaxy.

@@

One possible scenario that could possibly produce a large K enhanced signature, as well as the observed Na pattern, throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is some less massive star. The SAGB star produces K (destroying Na) which is then mixed into its envelope. It then deposits its K rich envelope onto its smaller companion through conventional binary accretion. This smaller and companion would continue to evolve long after the SAGB star is gone and, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, would not. If the companion star had sufficient mass to undergo hot bottom burning, then Na should be enhanced from production from \ce{^24 Mg} and \ce{^22 Ne}. In this scenario, it is this smaller binary companion star that makes up our sample of 113 giants. Note that since the envelope in a hot-bottom burning star is well mixed, the spectral signatures of these elements are observable.
